\documentclass{resume}

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Thor Lindberg, M.Sc. IT}
\address{hello@thor.computer \\ \href{https://github.com/thordotcomputer}{github.com/thordotcomputer}}

\begin{document}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

\begin{rSection}{Cover letter}
    With a background in IT and experience with ((experience)), I believe I would be a great candidate for the role of ((job)) at ((company)).

    A few traits that characterize me are:

    \begin{itemize}
        \item Motivated by learning and tasks that challenge my existing skill set.
        \item Focused on results, with continuous assessment of cost-benefit.
        \item Eager to take charge of meetings and responsibility for reaching goals.
    \end{itemize}

    In my previous role as an IT Consultant, I worked on software development for projects such as the national platform for secure communication in Denmark. In other projects I had sole responsibility for engaging clients in the pre-analysis and business process analysis phases of projects. This involved assessing the need for digital transformation through the analysis of existing business processes and the infrastructure changes necessary for meeting client goals.

    In a professional environment, I value:

    \begin{itemize}
        \item Planning tasks with transparent status reporting and risk mitigation.
        \item Documenting work and knowledge gained, ensuring it is always available for handover from one worker to another worker.
        \item Learning from experienced co-workers interested in sharing knowledge.
    \end{itemize}

    I am eager to learn more about the work culture at ((company)) and would appreciate the opportunity to discuss how I can contribute to your team. Please reach out to me if you think I would be suitable for this role or another position at ((company)).

    Thank you in advance for considering this application.
\end{rSection}

\end{document}