\documentclass{resume}

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Thor Lindberg, M.Sc. IT}
\address{hello@thor.computer \\ \href{https://github.com/thordotcomputer}{github.com/thordotcomputer}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EXECUTIVE SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
    {2+ years experience with business analysis, project management, and software development.}
    {An interdisciplinary profile with a background in design and agile development of IT systems and services, equipped with a broad perspective on IT and digital transformation for businesses, non-profits and government agencies.}
    {I am fluent in both English and Danish.}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
    \href{https://www.nordea.dk}{
        \textbf{IT Project Assistant}, Nordea
    }
    \hfill
    Taastrup, Denmark, 2024
    \begin{itemize}
        \item Responsible for data analysis and administration in access management group.
    \end{itemize}

    \href{https://netcompany.com}{
        \textbf{IT Consultant}, Netcompany
    }
    \hfill
    Copenhagen, Denmark, 2022 - 2023
    \begin{itemize}
        %        \item Implemented server-driven i18n localization in a React Native and React Native for Web application.
        %        \item Designed and implemented two-way XML to Java object data mapping.
        \item Contributed to software implementation on new and existing architectures, in Java and React Native.
        \item Authored feature specifications with UML diagrams for projects in collaboration with internal teams and clients.
        \item Managed client relations, planned and conducted design/technical workshops, and wrote Minutes of Meeting (MoM).
              %        \item Worked with GDPR compliance through design and development of IT systems.
        \item \textit{Impact:} Established healthy client relationships in new areas within the Finance and Government sector.
        \item \textit{Achievement:} Delivered 2 projects for 2 clients, meeting deadlines and agreed upon minimum viable product (MVP).
    \end{itemize}

    \href{https://politi.dk/en/about-the-police/national-special-crime-unit}{
        \textbf{IT-Administrative Student}, National Special Crime Unit
    }
    \hfill
    Copenhagen, Denmark, 2021 - 2022
    \begin{itemize}
        \item Managed and provided direct support to users of web portal. Authored documentation for web portal.
        \item \textit{Impact:} Improved data quality by assisting users in accurately reporting information.
    \end{itemize}

    \href{https://en.itu.dk}{
        \textbf{Teaching Assistant}, IT University of Copenhagen
    }
    \hfill
    Copenhagen, Denmark, 2021 - 2022
    \begin{itemize}
        \item Assisted with courses in UX Design, Experimental Design (JavaScript + MQTT), and Programming (Python).
    \end{itemize}

    \href{https://www.dominos.dk}{
        \textbf{Shift Leader}, Domino's Pizza
    }
    \hfill
    Lyngby, Denmark, 2021 - 2022
    \begin{itemize}
        \item Primary baker during rush hours. Managed store operations and inventory. Delegated work to drivers.
    \end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
    \href{https://en.itu.dk}{
        \textbf{Master of Science in Information Technology}, IT University of Copenhagen
    }
    \hfill
    2020 - 2022
    \begin{itemize}
        %        \item \textit{Thesis:} "Type-Extensible Object Notation: JSON with Syntax for Types" (JavaScript, TDD, UML)
        \item \href{https://learnit.itu.dk/local/coursebase/view.php?ciid=666}{Programming Mobile Applications (React Native, Expo, MapView, Firebase)}
        \item \href{https://learnit.itu.dk/local/coursebase/view.php?ciid=589}{Experimental Design in Practice (Distributed Network Interactions, JavaScript, Event Handlers, MQTT)}
        \item \href{https://learnit.itu.dk/local/coursebase/view.php?ciid=578}{Data Design (Tableau, Data Visualization, Data Graphs, Data-Driven Design)}
        \item \href{https://learnit.itu.dk/local/coursebase/view.php?ciid=487}{Advanced Design Processes (Double Diamond, Design Thinking, User-Centered Design, Prototyping, Arduino)}
        \item \href{https://learnit.itu.dk/local/coursebase/view.php?ciid=624}{UX Design I (Iterative Prototyping, Wireframing, Design Theory, Interface Paradigms, Usability Testing)}
        \item \href{https://learnit.itu.dk/local/coursebase/view.php?ciid=681}{UX Design II (Personas, UX Research, Engagement Design, Critical Reflection)}
        \item \textit{Article:} "Annotation Task Design in Medical Imaging" (LaTeX, Multiple Instance Learning, Multi-Task Learning)
    \end{itemize}

    \href{https://healthsciences.ku.dk}{
        \textbf{Bachelor of Science in Health Informatics}, Copenhagen University
    }
    \hfill
    2017 - 2020
    \begin{itemize}
        %        \item \textit{Project:} "Tools for Caretakers of Stroke Victims" (Qualitative Methods, Interviews, Co-Design Workshops)
        \item System Development and Databases (Java, SQL, OOP, Relational Databases, UML, Use Cases, Scrum, XML)
        \item \href{https://kurser.ku.dk/course/sitb17003u/2017-2018}{Statistical Methods (R, Probability Distributions, Estimation, Confidence Intervals, Significance Tests (p-values))}
        \item Mathematical Modelling and Programming (MATLAB, Vectors, Matrices, Linear Algebra, Simulation)
        \item \href{https://kurser.dtu.dk/course/22525}{Medical Image Analysis (MATLAB, Bitmap Image Processing (Matrices), Machine Learning (Blob Analysis))}
        \item \href{https://kurser.ku.dk/course/sbia10210u/2020-2021}{Applied Programming for Biosciences (Python with NumPy, Pandas, Matplotlib)}
        \item IT Security (Encryption/Decryption, Private/Public Keys, Phishing, Physical Security)
        \item Interaction Design (HCI, Affordance, Visibility (Gulf of Execution), Feedback (Gulf of Evaluation))
              %        \item Human Anatomy and Physiology (Cells, Metabolism, Organs, Neurons, Endocrine System, Pathogenesis, Etiology)
    \end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Certificates}
    \href{https://www.coursera.org/professional-certificates/meta-front-end-developer}{
        \textbf{Front-End Developer}, Meta
    }
    \hfill
    2024

    \href{https://www.coursera.org/learn/laravel-framework-and-php}{
        \textbf{Mastering Laravel Framework and PHP}, Board Infinity
    }
    \hfill
    2024
\end{rSection}

\end{document}